\latinwithdropcap{}{E}{xorcizamus}{ te, omnis immunde spiritus, omnis satanica potestas, omnis incursio infernalis adversarii, omnis legio, omnis congregatio et secta diabolica,  
}
\vernacularwithdropcap{}{I}{n the name }{of our Lord Jesus \grecross~Christ and by His power, we cast you out, every unclean spirit, every devilish power, every assault of the infernal adversary, 
}
\twoCols
{in nomine et virtute Domini Nostri Jesu \grecross~ Christi, eradicare et effugare a Dei Ecclesia, ab omnibus ad imaginem Dei conditis ac pretioso divini Agni sanguine redemptis \grecross. }
{every legion, every diabolical group and sect; begone and stay far from the Church of God, from all who are made in the image of God and redeemed by the precious blood of the divine \grecross~Lamb.}
\twoCols
{Non ultra audeas, serpens callidissime, decipere humanum ge\-nus, Dei Ecclesiam persequi, ac Dei electos excutere et cribrare sicut triticum \grecross.  
}{Never again dare, you cunning serpent, to deceive the human race, to persecute the Church of God, nor to strike the chosen of God and to sift them as \grecross~wheat. 
}
\twoCols
{Imperat tibi Deus altissimus \grecross, cui in magna tua superbia te similem haberi adhuc pr\ae sumis; qui omnes homines vult salvos fieri, et ad agnitionem veritatis venire. Imperat tibi Deus Pater \grecross. Imperat tibi Deus Filius \grecross. Imperat tibi Deus Spiritus Sanctus \grecross. 
}{For it is the Most High God who commands you, \grecross~He to whom you heretofore in your great pride considered yourself equal; He who desires that all men might be saved and come to the knowledge of truth. God the Father \grecross~commands you. God the Son \grecross~commands you. God the Holy \grecross~Spirit commands you. 
}
\twoCols
{Imperat tibi majestas Christi, \ae ternum Dei Verbum caro factum \grecross,  qui pro salute generis nostri tua invidia perditi,
}{The majesty of Christ, the eternal Word of God made flesh \grecross~commands you; He who for the salvation of our race, the race that was lost through your envy, 
}\twoCols
{ humiliavit semetipsum factus obediens usque ad mortem;
}{humbled Himself and became obedient even unto death;
}
\twoCols
{qui Ecclesiam suam \ae dificavit supra firmam petram, et portas inferi adversus eam nunquam esse pr\ae valituras edixit, et cum ea ipse permansurus omnibus diebus usque ad consummationem s\ae culi. Imperat tibi sacramentum Crucis \grecross, omniumque christian\ae \ fidei Mysteriorum virtus \grecross. Imperat tibi excelsa Dei Genitrix Virgo Maria \grecross, qu\ae \ superbissimum caput tuum a primo instanti immaculat\ae \ su\ae \ conceptionis in sua humilitate contrivit. }
{ He who built His Church upon a solid rock, and proclaimed that the gates of hell should never prevail against her, and that He would remain with her all days, even to the end of the world. The sacred mystery of the cross \grecross~commands you, as well as the power of all the mysteries of Christian faith. The exalted Virgin Mary, Mother of God \grecross~commands you, who in her lowliness crushed your proud head from the first moment of her Immaculate Conception. }
\twoCols
{Imperat tibi fides sanctorum Apostolorum Petri et Pauli, et ceterorum Apostolorum \grecross. Imperat tibi Martyrum sanguis, ac pia Sanctorum et Sanctarum omnium intercessio \grecross.
}{The faith of the holy apostles Peter and Paul and the other apostles \grecross~commands you. The blood of the martyrs and the devout intercession of all holy men and women commands you.
}
\twoCols
{Ergo, draco maledicte et omnis legio diabolica, adjuramus te per Deum \grecross~vivum, per Deum \grecross~verum, per Deum \grecross~sanctum, per Deum qui sic dilexit mundum, }
{Therefore, accursed dragon and every diabolical legion, we adjure you by the living \grecross~God, by the true \grecross~God, by the holy \grecross~God, by the God who so loved the world }
\twoCols
{ut Filium suum unigenitum daret,  ut omnes qui credit in eum non pereat, sed habeat vitam \ae ternam: cessa decipere humanas creaturas, eisque \ae tern\ae\  perditionis venenum propinare: desine Ecclesi\ae \ nocere, et ejus libertati laqueos injicere.
}{that He gave His only-begotten Son, that whoever believes in Him shall not perish but shall have life everlasting; cease your deception of the human race and your giving them to drink of the poison of everlasting damnation; desist from harming the Church and fettering her freedom. 
}
\twoCols
{Vade, satana, inventor et magister omnis fallaci\ae , hostis human\ae \ salutis. Da locum Christo, in quo nihil invenisti de operibus tuis; da locum Ecclesi\ae \ uni, sanct\ae , catholic\ae , et apostolic\ae , quam Christus ipse acquisivit sanguine suo. Humiliare sub potenti manu Dei; contremisce et effuge, invocato a nobis sancto et terribili nomine Jesu, quem inferi tremunt, cui Virtutes et Potestates et Dominationes subject\ae \ sunt;}
{Begone Satan, you father and teacher of lies and enemy of mankind. Give place to Christ in whom you found none of your works; give place to the one, holy, Catholic, and apostolic Church, which Christ Himself purchased with His blood. May you be brought low under Gods mighty hand.  May you tremble and flee as we call upon the holy and awesome name of Jesus, before whom hell quakes, and to whom the virtues, powers,}
\twoCols
{ quem Cherubim et Seraphim indefessis vocibus laudant, dicentes: Sanctus, Sanctus, Sanctus Dominus Deus Sabaoth.}
{ and dominations are subject; whom the cherubim and seraphim praise with unwearied voices, saying: Holy, holy, holy, Lord God of hosts!}

