%{\parskip1pt

\setgregorian1
\setclef13
\musicindent14mm
\raisesong3\Internote
\nosolesmescustos
\initiumgregorianum
\musicinitial{}{K}%
\sgn {}Yr\punctum c\egn
\sgn {}i-\punctum a\egn
\sgn {}e{}\engl{Lord have mercy.}\punctum a\egn
\spatium
\sgn {}e-\punctum a\egn
\sgn l{\e}-\punctum a\egn
\sgn {}i-\punctum N\egn
\sgn so{n. \it ij \rm}\punctum a\augmentum b\egn
\spatium
\divisiofinalis
\spatium
\sgn {Chr}{i}{st}\punctum c\egn
\sgn {}e{}\punctum a\egn
\spatium
\sgn {}e-\engl{Christ have mercy.}\punctum a\egn
\sgn l{\e}-\punctum a\egn
\sgn {}i-\punctum N\egn
\sgn so{n. \it ij \rm}\punctum a\augmentum b\egn
\spatium
\divisiofinalis
\spatium
\sgn K{\y}r\punctum c\egn
\sgn {}i-\punctum a\egn
\sgn {}e{}\engl{Lord}\punctum a\egn
\spatium
\custos b
\lineaproxima
\sgn {}e-\punctum a\egn
\sgn l{\e}-\punctum a\egn
\sgn {}i-\engl{have mercy.}\punctum N\egn
\sgn so{n. \it ij \rm}\punctum a\augmentum b\egn
\spatium
\divisiofinalis
\spatium
\sgn {Chr}{i}{st}\punctum c\egn
\sgn {}e{}\pes bc\egn
\spatium
\sgn {}{a}u\engl{Christ hear us.}\punctum a\egn
\sgn di{}\punctum b\egn
\spatium
\sgn no{s. \it ij \rm}\punctum c\augmentum d\egn
\spatium
\divisiofinalis
\spatium
\sgn {Chr}{i}{st}\punctum c\egn
\sgn {}e{}\punctum b\egn
\spatium
\sgn {}ex\engl{Christ graciously hear us.}\punctum c\egn
\sgn {}{\a}u\punctum a\egn
\sgn di{}\punctum b\egn
\spatium
\sgn no{s. \it ij \rm}\punctum c\augmentum d\egn
\spatium
\divisiofinalis
\spatium
\custos c
\lineaproxima
\sgn {\quad   P}{a}-\punctum c\egn
\sgn ter\punctum c\egn
\spatium
\sgn de{}\punctum c\egn
\spatium
\sgn c{\ae}l\engl{God the Father of heaven,}\punctum c\egn
\sgn {}is\punctum c\egn
\spatium
\sgn {\bf D}{\bf e}{\bf -}\punctum d\egn
\sgn {}u{s,}\punctum b\augmentum b\egn
\spatium
\fissum{5pt}
\divisiomaior
\spatium
\fissum{5pt}
\sgn mi-\punctum b\egn
\sgn se-\punctum b\egn
\sgn r{\e}-\punctum a\egn
\sgn re{}\engl{have mercy on us.}\punctum b\egn
\spatium
\sgn n{o}-\punctum c\egn
\sgn bi{s.}\punctum c\augmentum d\egn
\Finisgregoriana

\smallskip

%\vskip1mm

\lateng{2mm}{F{i}li Redemptor mundi {\bf De}us, miser\ere nobis.}{God the Son, Redeemer of the world, have mercy on us.}

\lateng{2mm}{Sp\\i ritus Sancte {\bf De}us, miser\ere nobis.}{God the Holy Spirit, have mercy on us.}

\lateng{2mm}{Sancta Tr\\i nitas unus {\bf De}us, mi\-se\-r\ere nobis.}{Holy Trinity, one God, have mercy on us.}

%\smallskip
\break

\setgregorian1
\setclef13
\musicindent2mm
\raisesong3\Internote
\nosolesmescustos
\initiumgregorianum
\sgn {\quad  S}{a}{nc}\punctum c\egn
\sgn ta{}\punctum c\egn
\spatium
\sgn Ma-\engl{Holy Mary,}\punctum c\egn
\sgn {\bf r}{\bf\\i}{\bf -}\punctum d\punctumcavum b\egn
\sgn {}a{,}\punctum b\augmentum b\egn
\spatium
\divisiomaior
\spatium
\sgn { }{o}-\punctum b\egn
\sgn ra{}\punctum a\egn
\spatium
\sgn {pr}o{}\engl{pray for us.}\punctum b\egn
\spatium
\sgn n{o}b\punctum c\egn
\sgn {}i{s.}\punctum c\augmentum d\egn
\spatium
\Finisgregoriana

%\vskip-5pt

%\hbox{\parindent2mm
%\vtop{
%\hsize65mm
%\ 

\smallskip

\lateng{2mm}{Sancta Dei {\bf G\e}nitrix, ~ ora pro nobis.}
{Holy Mother of God,}

\lateng{2mm}{Sancta Virgo {\bf v\\i}rginum, ora pro nobis.}
{Holy Virgin of virgins,}

%}
%\vrule
%\hskip5mm
%\vtop{
%\hsize42mm

\smallskip

\lateng{2mm}{Sancte {\bf M\\i}chael,}{Saint Michael,}

\lateng{2mm}{Sancte {\bf Ga}briel,}{Saint Gabriel,}

\lateng{2mm}{Sancte {\bf Ra}phael,}{Saint Raphael,}

%}}

\smallskip

\setgregorian1
\setclef13
\musicindent2mm
\raisesong3\Internote
\nosolesmescustos
\initiumgregorianum
\sgn {}Om\punctum c\egn
\sgn nes\punctum c\egn
\spatium
\sgn san\punctum c\egn
\sgn {ct}i{}\punctum c\egn
\spatium
\sgn {}An\punctum c\egn
\sgn gel\engl{All ye holy Angels and Archangels,}\punctum c\egn
\sgn {}i{}\punctum c\egn
\spatium
\sgn {}et\punctum c\egn
\spatium
\sgn {}Ar\punctum c\egn
\sgn {\bf ch}{\bf \a}{\rm n}\punctum d\egn
\sgn gel\punctum b\egn
\sgn {}i{}\punctum b\augmentum b\egn
\spatium
\divisiomaior
\spatium
\sgn { }{o}-\punctum b\egn
\sgn rat\punctum b\egn
\sgn {}e{}\punctum a\egn
\spatium
\sgn {pr}o{}\engl{pray for us.}\punctum b\egn
\spatium
\sgn n{o}-\punctum c\egn
\sgn bi{s.}\punctum c\augmentum d\egn
\spatium
\Finisgregoriana

\smallskip

\lateng{2mm}{Omnes sancti beatorum Spirituum {\bf \or}dines, orate pro nobis.}{All ye holy orders of blessed Spirits,}

\lateng{2mm}{Sancte Joannes Bap{\bf t\\i}sta, ora pro nobis.}{Saint John Baptist,}

\lateng{2mm}{Sancte {\bf Jo}seph, ora pro nobis.}{Saint Joseph,}

\lateng{2mm}{Omnes sancti Patri\arch\ae\ et Pro{\bf ph\e}t\ae , orate pro nobis.%\footnote{`ora for one saint, `orate for more than one.}
}{All ye holy Patriarchs and Prophets,}


\bigskip

%\hbox{\parindent2mm
%\vtop{
%\hsize52mm

\lateng{2mm}{Sancte {\bf Pe}tre, ora pro nobis.}{Saint Peter,}

\lateng{2mm}{Sancte {\bf Pau}le,}{Saint Paul,}

\lateng{2mm}{Sancte An{\bf dr\e}a,}{Saint Andrew,}

\lateng{2mm}{Sancte Ja{\bf c\o}be,}{Saint James,}

\lateng{2mm}{Sancte Jo{\bf \a}nnes,}{Saint John,}

\lateng{2mm}{Sancte {\bf Tho}ma,}{Saint Thomas,}


\lateng{2mm}{Sancte Ja{\bf c\o}be,}{Saint James,}

\lateng{2mm}{Sancte Phi{\bf l\\i}ppe,}{Saint Philip,}

%}
%\hskip5mm
%\vrule
%\hskip5mm
%\vtop{
%\hsize52mm


\lateng{2mm}{Sancte Bartholo{\bf m\\ae}e,}{Saint Bartholomew,}

\lateng{2mm}{Sancte Mat{\bf th\\ae}e,}{Saint Matthew,}

\lateng{2mm}{Sancte {\bf Si}mon,}{Saint Simon,}


\lateng{2mm}{Sancte Thad{\bf d\\ae}e,}{Saint Jude,}

\lateng{2mm}{Sancte Mat{\bf th\\i}a,}{Saint Matthias,}

\lateng{2mm}{Sancte {\bf B\ar}naba,}{Saint Barnabas,}

\lateng{2mm}{Sancte {\bf Lu}ca,}{Saint Luke,}

\lateng{2mm}{Sancte {\bf Mar}ce,}{Saint Mark,}

%}}

%\medskip

\lateng{2mm}{Omnes sancti Apostoli et Ev\-an\-ge{\bf l\\i}st\ae ,}{All ye holy Apostles and Evangelists,}

\lateng{2mm}{Omnes sancti Discipuli {\bf D\o}mini,}{All ye holy Disciples of the Lord,}


\smallskip

%\hbox{\parindent2mm
%\vtop{
%\hsize42mm

\lateng{2mm}{Omnes sancti Inno{\bf c\en}tes,}{All ye Holy Innocents,}

\lateng{2mm}{Sancte {\bf St\e}phane,}{Saint Stephen,}

\lateng{2mm}{Sancte Lau{\bf r\en}ti,}{Saint Lawrence,}

\lateng{2mm}{Sancte Vin{\bf c\en}ti,}{Saint Vincent,}

%}

%\vrule\hskip5mm

%\vtop{
%\hsize55mm

\lateng{2mm}{Sancti Fabi\ane et Sebasti{\bf \a}ne,}{Saint Fabian and Saint Sebastian,}

\lateng{2mm}{Sancti Jo\annes et {\bf Pau}le,}{Saint John and Saint Paul,}

\lateng{2mm}{Sancti Cosma et Dami{\bf \a}ne,}{Saint Cosmas and Saint Damian,}

\lateng{2mm}{Sancti Gerv\asi et Pro{\bf t\a}si,}{Saint Gervasius and Saint Protasius,}

%}}

%\medskip

\lateng{2mm}{Omnes sancti {\bf M\ar}tyres,}{All ye holy Martyrs,}

\bigskip

%\hbox{\parindent2mm
%\vtop{
%\hsize42mm

\lateng{2mm}{Sancte Sil{\bf v\es}ter,}{Saint Sylvester,}

\lateng{2mm}{Sancte Gre{\bf g\o}ri,}{Saint Gregory,}

\lateng{2mm}{Sancte Am{\bf br\o}si,}{Saint Ambrose,}

%}\vrule\hskip5mm
%\vtop{
%\hsize55mm


\lateng{2mm}{Sancte Augus{\bf t\\i}ne,}{Saint Augustine,}

\lateng{2mm}{Sancte Hie{\bf r\o}nyme,}{Saint Jerome,}

\lateng{2mm}{Sancte Mar{\bf t\\i}ne,}{Saint Martin,}

\lateng{2mm}{Sancte Nico{\bf l\a}\ae ,}{Saint Nicholas,}

%}}

%\smallskip

\lateng{2mm}{Omnes sancti Pontifices et Confes{\bf s\o}res,}{All ye holy Bishops and Confessors,}

\lateng{2mm}{Omnes sancti Doc{\bf t\o}res,}{All ye holy Doctors,}

\smallskip

%\hbox{\parindent2mm
%\vtop{
%\hsize42mm

\lateng{2mm}{Sancte An{\bf t\o}ni,}{Saint Anthony,}

\lateng{2mm}{Sancte Bene{\bf d\\i c}te,}{Saint Benedict,}

\lateng{2mm}{Sancte Ber{\bf n\ar}de,}{Saint Bernard,}
%}\vrule\hskip5mm
%\vtop{
%\hsize55mm

\lateng{2mm}{Sancte Do{\bf m\\i}nice,}{Saint Dominic,}

\lateng{2mm}{Sancte Fran{\bf c\\i s}ce,}{Saint Francis,}
%}
%}

%\medskip

\lateng{2mm}{Omnes sancti Sacerd\otes et Le{\bf v\\i}t\ae ,}{All ye holy Priests and Levites,}

\lateng{2mm}{Omnes sancti M\onachi et Ere{\bf m\\i}t\ae ,}{All ye holy Monks and Hermits,}

\bigskip

%\hbox{\parindent2mm
%\vtop{
%\hsize42mm

\lateng{2mm}{Sancta Maria Magda{\bf l\e}na,}{Saint Mary Magdalene,}

\lateng{2mm}{Sancta {\bf A}gatha,}{Saint Agatha,}

\lateng{2mm}{Sancta {\bf L\u}cia,}{Saint Lucy,}

\lateng{2mm}{Sancta {\bf Ag}nes,}{Saint Agnes,}

%}\vrule\hskip5mm
%\vtop{
%\hsize55mm

\lateng{2mm}{Sancta C\ae {\bf c\\i}lia,}{Saint Cecilia,}

\lateng{2mm}{Sancta Catha{\bf r\\i}na,}{Saint Catherine,}

\lateng{2mm}{Sancta Anas{\bf t\a}sia,}{Saint Anastasia,}

%}}

%\medskip

\lateng{2mm}{Omnes sanct\ae\ V\\i rgines et {\bf V\\i}du\ae ,}{All ye holy Virgins and Widows,}

\lateng{2mm}{ Omnes Sancti et Sanct\ae\ {\bf De}i, interc\edite pro nobis.}{ All ye Holy, Righteous, and Elect of God, intercede for us.}

\medskip
%\filbreak

\setgregorian1
\setclef13
\musicindent0mm
\raisesong3\Internote
\nosolesmescustos
\initiumgregorianum
\sgn {Pr}op\punctum c\egn
\sgn {}{\\i}{\it t}\punctum c\egn
\sgn {}{\it i}{-}\punctum b\egn
%\sgn {}{\it u}{\it s}\cchar{-10}{\it{Be Thou merciful,}}\cchar{-7}{Prop\\i{\it ti-us} {\bf e}sto, ~}\punctum a\egn
\sgn {}{\it u}{\it s}\engl{Be Thou merciful,}\punctum a\egn
\spatium
\sgn {}{\bf e}s\punctum c\egn
\sgn {t}o{,}\punctum d\augmentum d\egn
\spatium
\divisiomaior
\spatium
\sgn par\punctum b\egn
\sgn ce{}\punctum c\egn
\spatium
\sgn n{o}-\engl{spare us, O Lord.}\punctum a\egn
%\sgn bi{s,}\cchar{-7}{ex\audi nos, D\omine.}\punctum N\egn
\sgn bi{s,}\punctum N\egn
\spatium
\sgn D{\o}m\punctum a\egn
\sgn {}in\punctum N\egn
%\sgn {}e.\rchar{-7}{\textit{\qquad graciously hear us, O Lord.}}\rchar{-4}{\textit{\qquad spare us, O Lord.}}\punctum M\augmentum N\egn
\sgn {}e.\punctum M\augmentum N\egn
\spatium
\Finisgregoriana

\bigskip

\lateng{2mm}{Prop\\i{\it ti-us} {\bf e}sto, ~ex\audi nos, D\omine.}{Be Thou merciful, graciously hear us, O Lord.}


\setgregorian1
\setclef13
\musicindent0mm
\raisesong3\Internote
\nosolesmescustos
\initiumgregorianum
\sgn {}Ab\punctum c\egn
\spatium
\sgn {}{\it o}{\it m}\punctum b\egn
\sgn {\it n}{\it i}{}\engl{From all evil,}\punctum a\egn
\spatium
\sgn {\bf m}{\bf a}-\punctum c\punctumcavum d\egn
\sgn {l}o{,}\punctum d\augmentum d\egn
\spatium
\divisiomaior
\spatium
\sgn l{\\i}b\punctum b\egn
\sgn {}e{r}\punctum c\egn
\sgn {}a{}\punctum a\egn
\spatium
\sgn no{s,}\engl{deliver us, O Lord.}\punctum N\egn
\spatium
\sgn D{\o}m\punctum a\egn
\sgn {}in\punctum N\egn
\sgn {}e.\punctum M\augmentum N\egn
\spatium
\Finisgregoriana

\medskip

\lateng{2mm}{Ab o{\it mni pec}{\bf c\a}to, l\\i bera nos D\omine.}{From all deadly sin,}

\lateng{2mm}{Ab {\it ira} {\bf tu}a, l\\i bera nos D\omine.}{From thine anger,}

\lateng{2mm}{A subit\anea et impro{\it v\\i sa} {\bf mor}te,}{From sudden and unrepentant death,}

\lateng{2mm}{Ab ins\\i di{\it is di}{\bf \a}boli,}{From the crafts and assaults of the devil,}

\lateng{2mm}{Ab ira, et \odio, et omni mala {\it volun}{\bf t\a}te,}{From anger, and hatred, and all un\-cha\-ri\-ta\-ble\-ness,}

\lateng{2mm}{A sp\\i ritu forni{\it cati}{\bf \o}nis,}{From the spirit of fornication,}

\lateng{2mm}{A f\ulgure et {\it tempes}{\bf t\a}te,}{From lightning and tempest,}

\lateng{2mm}{A flag\ello {\it terr\ae}{\bf m\o}tus,}{From the peril of earthquake, fire, and flood,}

\lateng{2mm}{A peste, fa{\it me et} {\bf bel}lo,}{From pestilence, famine, and battle,}

\lateng{2mm}{A mor{\it te per}{\bf p\e}tua,}{From everlasting damnation,}

\lateng{2mm}{Per myst\erium sanct\ae\ Incarnati{\it \onis} {\bf tu}\ae ,}{By the mystery of Thy holy Incarnation,}

\lateng{2mm}{Per Ad{\it v\entum} {\bf tu}um,}{By Thine Advent,}

\lateng{2mm}{Per Nativi{\it t\atem} {\bf tu}am,}{By Thy Nativity,}

\lateng{2mm}{Per Bapt\\i smum et sanctum Je\-j\u\-{\it nium} {\bf tu}um,}{By Thy Baptism and holy Fasting,}

\lateng{2mm}{Per Crucem et Passi{\it \onem} {\bf tu}am,}{By Thy Cross and Passion,}

\lateng{2mm}{Per Mortem et Sepul{\it t\uram} {\bf tu}am,}{By Thy precious Death and Burial,}

\lateng{2mm}{Per sanctam Resurrecti{\it \onem} {\bf tu}am,}{By Thy holy Resurrection,}

\lateng{2mm}{Per admir\abilem Ascensi{\it \onem} {\bf tu}am,}{By Thy glorious Ascension,}

\lateng{2mm}{Per adv\entum Sp\\i ritus Sanc{\it ti} Pa{\bf r\a}cliti,}{By the coming of the Holy Ghost the Comforter,}

\lateng{2mm}{In di{\it e ju}{\bf d\\i}cii,}{In the day of judgement,}


\bigskip

%\bigskip

\setgregorian1
\setclef13
\musicindent0mm
\raisesong3\Internote
\nosolesmescustos
\initiumgregorianum
\sgn Pec\punctum c\egn
\sgn {\it c}{\it a}-\engl{Sinners,}\punctum b\egn
\sgn {\bf t}{\bf \o}-\punctum d\punctumcavum e\egn
\sgn re{s,}\punctum e\augmentum f\egn
\spatium
\divisiomaior
\spatium
\sgn te{}\punctum c\egn
\spatium
\sgn rog\punctum b\egn
\sgn {}{\a}m\punctum a\egn
\sgn {}us\punctum N\egn
\spatium
\sgn {}{a}u\engl{we beseech Thee, hear us.}\punctum a\egn
\sgn di{}\punctum b\egn
\spatium
\sgn no{s,}\punctum c\augmentum d\egn
\spatium
\Finisgregoriana

\bigskip

\parindent0mm

\lateng{2mm}{Ut no{\it bis} {\bf par}cas, te rog\amus audi nos.}{That Thou wouldst spare us,}

\lateng{2mm}{Ut nobis {\it in}{\bf d\ul}geas, te rog\amus audi nos.}{That Thou wouldst pardon us,}

\lateng{2mm}{Ut ad veram p\ae nit\entiam nos per\-d\u\-cere {\it di}{\bf gn\e}ris,}{That Thou wouldst give us true repentance,}

\lateng{2mm}{Ut Eccl\esiam tuam sanctam  r\egere et conserv\are {\it di}{\bf gn\e}ris,}{That Thou wouldst rule and govern Thy holy Church,}

\lateng{2mm}{Ut Domnum Apost\olicum et omnes ecclesi\asticos \ordines  in %\qquad 
sancta religi\one conserv\are {\it di}{\bf gn\e}ris,}{That Thou wouldst preserve the household of the Apostles, and to keep all orders in the Church in Thy true religion,}
 
\lateng{2mm}{Ut inim\\i cos sanct\ae\  Eccl\esi\ae\  humili\are {\it di}{\bf gn\e}ris,}{That Thou wouldst humble the enemies of Thy holy Church,}

\lateng{2mm}{Ut r\egibus et princ\\i pibus chris\-ti\-\anis  pacem et veram con\-c\or\-diam 
don\are {\it di}{\bf gn\e}ris,}{That Thou wouldst bestow on all Christian kings and princes true peace and concord,}

%\loreto{\quad true peace and concord,}

\lateng{2mm}{Ut cuncto p\opulo christi\ano  pacem et unit\atem larg\\i ri {\it di}{\bf gn\e}ris,}{That Thou wouldst give to all Christian nations peace and unity,}

\lateng{2mm}{Ut omnes err\antes ad unit\atem Ec\-cl\e\-si\ae\ revocare,  et infid\eles
univ\ersos ad Evang\elii lumen perd\ucere {\it di}{\bf gn\e}ris,}{That Thou wouldst restore unity to Thy Church, and to lead all unbelievers into the light of Thy holy Gospel,}

%\loreto{\quad unbelievers into the light of Thy holy Gospel,}

\lateng{2mm}{Ut nosmet\\i psos in tuo sancto serv\\i tio  confort\are et conserv\are
{\it di}{\bf gn\e}ris,}{That Thou wouldst strengthen and preserve us in Thy holy service,}

\lateng{2mm}{Ut mentes nostras  ad c\ae l\estia desid\eri{\it a} {\bf \e}rigas,}{That Thou wouldst lift up our minds to heavenly desires,}

\lateng{2mm}{Ut \omnibus benefact\oribus nostris  sempit\erna bona {\it re}{\bf tr\\i}buas,}{That Thou wouldst render eternal blessings to all our benefactors,}

\lateng{2mm}{Ut \animas nostras,  fratrum, pro\-pin\-qu\o\-rum et benefact\orum
nostr\orum  ab \ae t\erna dam\-na\-ti\-\one {\it e}{\bf r\\i}pias,}{That Thou wouldst deliver from eternal damnation our souls, and those of our brethren, kindred, and benefactors,}

%\loreto{\quad those of our brethren, kindred, and benefactors,}

\lateng{2mm}{Ut fructus terr\ae\  dare et conserv\are {\it di}{\bf gn\e}ris,}{That Thou wouldst give and preserve  the  fruits of the earth,}

\lateng{2mm}{Ut \omnibus fid\elibus def\unctis  r\e\-quiem \ae t\ernam don\are {\it di}\-{\bf gn\e}\-ris,}{That Thou wouldst grant to all Thy faithful departed eternal rest,}

\rubrics{The Celebrant sings:}

\lateng{2mm}{Ut hanc aquam bene + d\\i \-cere {\it di}\-{\bf gn\e}\-ris,}{That Thou wouldst bless this water}

\lateng{2mm}{Ut hanc aquam bene + d\\i \-cere et sanc\-ti + fic\are {\it di}\-{\bf gn\e}\-ris,}{That Thou wouldst bless and sanctify this water}

\rubrics{The Cantors continue:}

\lateng{2mm}{Ut nos exaud\\i re {\it di}{\bf gn\e}ris,}{That Thou wouldst graciously hear our prayer,}

\lateng{2mm}{Fi{\it li} {\bf De}i,}{O Son of God,}

\bigskip

\setgregorian1
\setclef13
\musicindent0mm
\raisesong3\Internote
\nosolesmescustos
\initiumgregorianum
\sgn {}Ag\punctum c\egn
\sgn nus\engl{Lamb of God,}\punctum c\egn
\spatium
\sgn D{e}-\pes cd\egn
\sgn {}i,\punctum d\augmentum d\egn
\spatium
\divisiominima
\spatium
\sgn {qu}i{}\punctum d\egn
\spatium
\sgn t{o}l\punctum d\egn
\sgn lis\punctum d\egn
\spatium
\sgn pec\punctum c\egn
\sgn c{\a}-\engl{~ who takes away the sin of the world,}\punctum d\egn
\sgn {t}a{}\bmolle b\punctum b\egn
\spatium
\sgn m{u}n\punctum c\egn
\sgn di,\punctum d\augmentum d\egn
\spatium
\divisiomaior
\spatium
\sgn p{a}r\punctum c\egn
\sgn ce{}\punctum d\egn
\spatium
\sgn n{o}b\punctum e\egn
\sgn {}is\engl{spare us,}\punctum c\egn
\spatium
\sgn D{\o}-\punctum d\egn
\custos a
\lineaproxima
\sgn min\engl{O Lord.}\punctum c\egn
\sgn {}e.\punctum c\augmentum d\egn
\spatium
\divisiofinalis
\spatium
\sgn {}Ag\punctum c\egn
\sgn nus\engl{Lamb of God,}\punctum c\egn
\spatium
\sgn D{e}-\pes cd\egn
\sgn {}i,\punctum d\augmentum d\egn
\spatium
\divisiominima
\spatium
\sgn {qu}i{}\punctum d\egn
\spatium
\sgn t{o}l\punctum d\egn
\sgn lis\punctum d\egn
\spatium
\sgn pec\punctum c\egn
\sgn c{\a}-\engl{who takes away the sin of the world, ~ }\punctum d\egn
\sgn {t}a{}\bmolle b\punctum b\egn
\spatium
\sgn m{u}n\punctum c\egn
\sgn di,\punctum d\augmentum d\egn
\spatium
\divisiomaior
\spatium
\sgn {}ex\punctum c\egn
\sgn {}{\a}u\punctum d\egn
\sgn di{}\engl{graciously}\punctum e\egn
\spatium
\custos b
\lineaproxima
\sgn nos\punctum c\egn
\spatium
\sgn D{\o}-\engl{hear us, O Lord.}\punctum d\egn
\sgn min\punctum c\egn
\sgn {}e.\punctum c\augmentum d\egn
\spatium
\divisiofinalis
\spatium
\sgn {}Ag\punctum c\egn
\sgn nus\engl{Lamb of God,}\punctum c\egn
\spatium
\sgn D{e}-\pes cd\egn
\sgn {}i,\punctum d\augmentum d\egn
\spatium
\divisiominima
\spatium
\sgn {qu}i{}\punctum d\egn
\spatium
\sgn t{o}l\punctum d\egn
\sgn lis\punctum d\egn
\spatium
\sgn pec\engl{~ who takes away the sin of the world,}\punctum c\egn
\sgn c{\a}-\punctum d\egn
\sgn {t}a{}\bmolle b\punctum b\egn
\spatium
\sgn m{u}n\punctum c\egn
\sgn di,\punctum d\augmentum d\egn
\spatium
\divisiomaior
\spatium
\custos c
\lineaproxima
\sgn mis\punctum c\egn
\sgn {}er\punctum d\egn
\sgn {}{\e}r\engl{have mercy on us.}\punctum e\egn
\sgn {}e{}\punctum c\egn
\spatium
\sgn n{o}-\punctum d\egn
\sgn {b}i{s.}\punctum c\augmentum d\egn
\spatium
\divisiofinalis
\spatium
\sgn {Chr}{i}{st}\punctum d\egn
\sgn {}e{}\pes cd\egn
\spatium
\sgn {}{a}u\engl{Christ hear us.}\bmolle b\punctum b\egn
\sgn di{}\punctum c\egn
\spatium
\sgn nos\punctum d\augmentum d\egn
\spatium
\divisiofinalis
\spatium
\sgn {Chr}{i}{st}\punctum d\egn
\sgn {}e{}\punctum c\egn
\spatium
\sgn {}ex\engl{Christ graciously hear us.}\punctum d\egn
\sgn {}{\a}u\bmolle b\punctum b\egn
\sgn di{}\punctum c\egn
\spatium
\sgn nos\punctum d\augmentum d\egn
\spatium
\divisiofinalis
\spatium\custos c\lineaproxima
\sgn K{\y}r\punctum c\egn
\sgn {}i-\punctum a\egn
\sgn {}e{}\engl{}\punctum a\egn
\spatium
\sgn {}e-\engl{Lord have mercy.}\punctum a\egn
\sgn l{\e}-\punctum a\egn
\sgn {}i-\punctum N\egn
\sgn so{n.}\punctum a\augmentum b\egn
\spatium
\divisiofinalis
\spatium
\sgn {Chr}{i}{st}\punctum c\egn
\sgn {}e{}\punctum a\egn
\spatium
\sgn {}e-\engl{Christ have mercy.}\punctum a\egn
\sgn l{\e}-\punctum a\egn
\sgn {}i-\punctum N\egn
\sgn so{n.}\punctum a\augmentum b\egn
\spatium
\divisiofinalis
\spatium
\sgn K{\y}r\punctum a\egn
\sgn {}i-\punctum N\egn
\sgn {}e{}\engl{}\pes Ma\egn
\spatium
\sgn {}e-\engl{Lord have mercy.}\bmolle b\clivis bN\egn
\sgn l{\e}-\punctum a\egn
\sgn {}i-\punctum N\egn
\sgn so{n.}\climacus NML\augmentum L\egn
\spatium\divisiofinalis\custos c\lineaproxima
\sgn P{\a}t\punctum c\egn
\sgn {}er\punctum c\egn
\spatium
\sgn n{\o}{st}\engl{Our Father}\punctum c\egn
\sgn {}e{r.   }\punctum a\augmentum b\egn
\spatium
\divisiofinalis
\spatium
\sgn {{\it secreto.} \s V.}Et\punctum c\egn
\spatium
\sgn ne{}\punctum c\egn
\spatium
\sgn nos\punctum c\egn
\spatium
\sgn {}i{nd}\punctum c\egn
\sgn {}{\u}c\engl{And lead us not into temptation}\punctum c\egn
\sgn {}as\punctum c\egn
\spatium
\sgn {}in\punctum c\egn
\spatium
\sgn te{nt}\punctum c\egn
\sgn {}at\punctum c\egn
\sgn {}i-\punctum c\egn
\sgn {}{\o}n\punctum c\egn
\sgn {}e{m.}\punctum a\augmentum b\egn
\spatium\divisiofinalis\custos c\lineaproxima
\sgn {\s R. S}ed\punctum c\egn
\spatium
\sgn l{\\i }b\punctum c\egn
\sgn {}er\punctum c\egn
\sgn {}a{}\engl{But deliver us from evil.}\punctum c\egn
\spatium
\sgn nos\punctum c\egn
\spatium 
\sgn {}a{}\punctum c\egn
\spatium
\sgn m{\a}-\punctum c\egn
\sgn lo.\punctum a\augmentum b\egn
\setemptybar
\Finisgregoriana

\bigskip