
\setgregorian1
\setclef14
\raisesong3
\Internote
\musicindent10mm
\initiumgregorianum
\musicinitial{VIII G*}{}%
\sgn Mag\punctum N\egn
\sgn n{\\i}-\clivis aN\egn
\sgn fi-\pes Nc\egn
\sgn ca{t   *}\punctum c\augmentum d\egn
\spatium\divisiomaior\spatium
\sgn { }{\a}n\punctum c\egn
\sgn {}im\punctum c\egn
\sgn {}a{}\engl{My soul doth magnify * the Lord,}\punctum c\egn
\spatium
\sgn {\it m}{\it \e}-\punctum b\egn
\sgn {}{\it a}{}\punctum c\egn
\spatium
\sgn {\bf D}{\bf \o}{\rm m}\punctum a\egn
\sgn {}in\punctumcavum N\egn
\sgn {}u{m.}\pes Na\augmentumduplex Nb\egn
\spatium
\setemptybar\custos N\lineaproxima
\sgn {}Et\punctum N\egn
\spatium
\sgn {}e{xs}\punctum a\egn
\sgn {}u{lt}\punctum c\egn
\sgn {}{\a}v\punctum c\egn
\sgn {}it\punctum c\egn
\spatium
\sgn {sp}{\\i }-\engl{and my spirit hath rejoiced}\punctum c\egn
\sgn ri-\punctum c\egn
\sgn tus\punctum c\egn
\spatium
\sgn {\bf m}{\bf \e}-\punctum d\egn
\sgn {  }{  }{  }\punctumcavum c\egn
\sgn {}u{s *}\punctum c\augmentum d\egn
\spatium\divisiomaior\spatium
\sgn {}in\punctum c\egn
\spatium
\sgn D{\e}-\punctum c\egn
\sgn {}o{}\punctum c\egn
\spatium
\sgn sa-\punctum c\egn
\sgn lu{}\punctum c\egn
\sgn {\it t}{\it \a}{\it r}\engl{in God my Saviour}\punctum b\egn
\sgn {}{\it i}{}\punctum c\egn
\spatium
\sgn {\bf m}{\bf \e}-\punctum a\egn
\sgn {  }{  }{  }\punctumcavum N\egn
\sgn {}o.\pes Na\augmentumduplex Nb\egn
%\setemptybar
\Finisgregoriana

\bigskip

%\lateng{0mm}{et exultavit spiritus meus * in Deo salvatore meo,}{and my spirit hath rejoiced * in God my Savior.}

\lateng{0mm}{Quia resp\exit humilit\atem anc\\i llae {\bf s\u}ae. *~ecce enim ex hoc be\atam me dicent \omnes gene{\it rati}{\bf \o}nes.}{For He hath regarded the humility of His handmaiden.* for behold, from henceforth all generations shall call me blessed.}

\lateng{0mm}{Quia fecit mihi magna, qui {\bf po}tens est,*~et sanctum {\it nomen} {\bf e}jus.}{For He that is mighty hath done great things to me, * and holy is His Name.}

\lateng{0mm}{Et miseric\ordia ejus a prog\enie in pro{\bf g\e}nies *~tim\en{\it tibus} {\bf e}um.}{And His Mercy is from generation unto generations * upon them that fear Him.}

\lateng{0mm}{Fecit pot\entiam in br\achio {\bf su}o, *~dis\-p\er\-sit sup\erbos mente {\it cordis} {\bf su}i.}{He hath shewed might in His arm, * He hath scattered the proud in the conceit of their heart.}

\lateng{0mm}{Dep\osuit pot\entes de {\bf se}de *~et exal{\it t\avit} {\bf h\u}miles;}{He hath put down the mighty from their seat, * and hath exalted the humble.}

\lateng{0mm}{Esuri\entes impl\evit {\bf bo}nis *~et d\\i vites dim\\i {\it sit in}{\bf \a}nes.}{He hath filled the hungry with good things, *
and the rich He hath sent empty away.}

\lateng{0mm}{Susc\epit Israel p\uerum {\bf su}um, *~recor\-d\a\-tus miseric\or{\it diae} {\bf su}ae,}{He hath received Israel, His servant, *
being mindful of His mercy.}

\lateng{0mm}{Sicut loc\utus est ad patres {\bf no}stros, *~Abraham et s\emini e{\it jus in} {\bf s\\ae }cula.}{As He spoke to our Fathers, *
Abraham and his seed forever.}

\lateng{0mm}{Gl\oria Patri, et {\bf F\\i }lio, *~et Spir\\i {\it tui} {\bf San}cto.}{Glory be to the Father, and to the Son, *~and to the Holy Spirit,}

\lateng{0mm}{Sicut erat in princ\\i pio, et nunc, et {\bf sem}per, *~et in s\\ae cula s\ae cu{\it l\orum}. {\bf A}men.}{As it was in the beginning, is now, and ever shall be, *~world without end. Amen.}