\lateng{0mm}{1 Laud\ate D\ominum, qu\oniam bonus {\it est} {\bf psal}mus; *~Deo nostro sit juc\unda, decor\a{\it que lau}{\bf d\a}tio.}{Praise the Lord, for He is good; * sing praise to our God, for He is gracious; it is fitting to praise Him.}

\lateng{0mm}{2 \AE d\\i ficans Jer\usa{\it lem} {\bf D\o}minus : *~dispersi\ones Isra\elis {\it congre}{\bf g\a}bit:}{The Lord rebuilds Jerusalem; * the dispersed of Israel He gathers.}

\lateng{0mm}{3 Qui sanat contr\\i {\it tos} {\bf cor}de, *~et \alligat contriti\o{\it nes e}{\bf \o}rum;}{He heals the brokenhearted * and binds up their wounds.}

\lateng{0mm}{4 Qui n\umerat multit\udinem {\it stel}{\bf l\a}rum : *~et \omnibus eis n\o{\it mina} {\bf vo}cat.}{He tells the number of the stars; * He calls each by name.}

\lateng{0mm}{5 Magnus D\ominus noster, et magna vir{\it tus} {\bf e}jus : *~et sapi\enti\ae \ ejus {\it non est} {\bf n\u}merus.}{Great is our Lord and mighty in power; * to His wisdom there is no limit.}

\lateng{0mm}{6 Susc\\i piens mansu\e{\it tos} {\bf D\o}minus : *~hum\\i lians autem peccat\ores us{\it que ad} {\bf ter}ram.}{The Lord sustains the lowly; * the wicked He casts to the ground.}

\lateng{0mm}{7 Pr\ae c\\i nite D\omino in confes{\it si}{\bf \o}ne : *~ps\allite Deo nos{\it tro in} {\bf c\\i }thara.}{Sing to the Lord with thanksgiving; * sing praise with the harp to our God.}

\lateng{0mm}{8 Qui \operit c\ae lum {\it n\u}{\bf bi}bus : *~et parat {\it terr\ae } {\bf pl\u}viam.}{Who covers the heavens with clouds, * who provides rain for the earth;}

\lateng{0mm}{9 Qui prod\ucit in m\onti{\it bus} {\bf f\oe }\-num : *~et herbam servi{\it t\uti} {\bf h\o}minum.}{Who makes grass sprout on the mountains * and herbs for the service of men;}

\lateng{0mm}{10 Qui dat jum\entis escam {\it ip}\-{\bf s\o}\-rum : *~et pullis corv\orum invoc\an{\it tibus} {\bf e}um.}{Who gives food to the cattle, * and to the young ravens when they cry to Him.}

\lateng{0mm}{11 Non in fortit\udine equi volunt\atem {\it ha}{\bf b\e}bit : *~nec in t\\i biis viri bene\-pl\ac\-itum {\it erit} {\bf e}i.}{He delights not in the strength of the steed, * nor is He pleased with the fleetness of men.}

\lateng{0mm}{12 Benepl\acitum est D\omino super tim\en{\it tes} {\bf e}um, *~et in eis, qui sperant super miseric\or{\it dia} {\bf e}jus.}{The Lord is pleased with those who fear Him, * with those who hope for His kindness.}

\lateng{0mm}{13 Gl\oria Patri, {\it et}  {\bf F\\i  }lio, *~et Spir\\i {\it tui} {\bf San}cto.}{Glory be to the Father, and to the Son, *~and to the Holy Spirit,}

\lateng{0mm}{14 Sicut erat in princ\\i pio, et nunc, {\it et} {\bf sem}per, *~et in s\\ae cula s\ae cu{\it l\orum.} {\bf A}men.}{As it was in the beginning, is now, and ever shall be, *~world without end. Amen.}
