\setgregorian1
\setclef14
\musicindent3mm
\raisesong3\Internote
\nosolesmescustos
\initiumgregorianum
\musicinitial{VI}{}%
\sgn {}A{ff}\punctum a\egn
\sgn {}{\e}{rt}\punctum a\egn
\sgn {}e{}\punctum a\egn
\spatium
\sgn D{\o}m\punctum a\egn
\sgn {}in\engl{Give to the Lord, you sons of God}\punctum a\egn
\sgn {}o,\punctum a\egn
\spatium
\sgn f{\\i }-\punctum a\egn
\sgn li-\punctum a\egn
\sgn {}{\it i}{}\punctum N\egn
\spatium
\sgn {\bf D}{\bf e}-\punctum a\egn
\sgn {}{}{}\punctumcavum M\egn
\sgn {}i{:  *}\punctum M\egn
\spatium
\divisiomaior\spatium
\sgn {}a{ff}\punctum a\egn
\sgn {}{\e}{rt}\punctum a\egn
\sgn {}e{}\punctum a\egn
\spatium
%\custos a\lineaproxima
\sgn D{\o}m\punctum a\egn
\sgn {}i-\punctum a\egn
\sgn no{}\engl{give to the Lord glory and praise,}\punctum a\egn
\spatium
\sgn f{\\i }-\punctum a\egn
\sgn li-\punctum a\egn
\sgn {}{\it o}{\it s}\punctum M\egn
\spatium
\sgn {}{\it a}{\it r}\pes Na\egn
\sgn {}{\bf i}-\punctum N\egn
\sgn {}et\punctumcavum M\egn
\sgn {}u{m.}\punctum M\egn
\setemptybar
\Finisgregoriana

\bigskip

%\lateng{0mm}{1 Aff\erte D\omino, f\\i lii Dei, *~aff\erte D\omino fil\\i os ari\etum.}{Give to the Lord, you sons of God, * give to the Lord %%glory and praise,}

\lateng{0mm}{2 Aff\erte D\omino gl\oriam et hon\orem; \dag ~aff\erte D\omino gl\o\-ri\-am nom\\i {\it ni} {\bf e}jus; *~ador\ate D\ominum in \atrio {\it sancto} {\bf e}jus.}{Give to the Lord the glory due His name; * adore the Lord in holy attire.}

\lateng{0mm}{3 Vox D\omini super \aquas; \dag ~De\-us ma\-jes\-t\a\-tis {\it in}\-{\bf t\o}\-nuit: *~D\ominus super {\it \aquas} {\bf mul}tas.}{The voice of the Lord is over the waters, the God of glory thunders, * the Lord, over vast waters.}

\lateng{0mm}{4 Vox D\omini in {\it vir}{\bf t\u}te; *~vox D\omini in mag{\it nifi}{\bf c\en}tia.}{The voice of the Lord is mighty; * the voice of the Lord is majestic.}

\lateng{0mm}{5 Vox D\omini confring\en{\it tis} {\bf ce}dros, *~et confr\inget D\ominus  ced{\it ros Li}{\bf b\a}ni:}{The voice of the Lord breaks the cedars, * the Lord breaks the cedars of Lebanon.}

\lateng{0mm}{6 Et comm\\i nuet eas, tamquam v\\i tulum {\it Li}{\bf b\a}ni, *~et dil\ectus quemadm\odum f\\i lius {\it uni}{\bf c\or}nium.}{He makes Lebanon leap like a calf * and Sarion like a young wild bull.}

\lateng{0mm}{7 Vox D\omini intercid\entis flammam ignis; \dag ~Vox D\omini concuti\entis {\it de}{\bf s\er}tum: *~et com\-m\o\-ve\-bit D\ominus de{\it s\ertum} {\bf Ca}des.}{The voice of the Lord strikes fiery flames; the voice of the Lord shakes the desert, * the Lord shakes the wilderness of Cades.}

\lateng{0mm}{8 Vox D\omini pr\ae par\antis cervos: \dag ~et revel\abit {\it con}{\bf d\en}sa, *~et in templo ejus omnes {\it dicent} {\bf gl\o}riam.}{The voice of the Lord twists the oaks and strips the forests, * and in His temple all say, "Glory!"}

\lateng{0mm}{9 D\ominus dil\uvium inhabita{\it re} {\bf fa}cit, *~et sed\ebit D\ominus rex {\it in \ae }{\bf t\er}num.}{The Lord is enthroned above the flood; * the Lord is enthroned as king forever.}

\lateng{0mm}{10 D\ominus virt\utem p\opulo su{\it o} {\bf da}bit; *~D\ominus bened\\i cet p\o\-pu\-lo {\it suo} {\bf in} pace.}{May the Lord give strength to His people; * may the Lord bless his people with peace.}

\lateng{0mm}{11 Gl\oria Patri, {\it et}  {\bf F\\i  }lio, *~et Spir\\i {\it tui} {\bf San}cto.}{Glory be to the Father, and to the Son, *~and to the Holy Spirit,}

\lateng{0mm}{12 Sicut erat in princ\\i pio, et nunc, {\it et} {\bf sem}per, *~et in s\\ae cula s\ae cu{\it l\orum.} {\bf A}men.}{As it was in the beginning, is now, and ever shall be, *~world without end. Amen.}

