\lateng{0mm}{1 Deus noster ref\ugium {\it et} {\bf vir}tus; *~adj\utor in tribulati\onibus qu\ae \ inven\e{\it runt nos} {\bf ni}mis.}{God is our refuge and our strength, * an ever-present help in distress.}

\lateng{0mm}{2 Propt\erea non tim\ebimus dum tur\-b\a\-bi\-{\it tur} {\bf ter}ra: *~et trans\-fe\-r\en\-tur montes {\it in cor} {\bf ma}ris.}{Therefore we fear not, though the earth be shaken and mountains plunge into the depths of the sea;}

\lateng{0mm}{3 Sonu\erunt, et turb\at\ae \ sunt aqu\ae \ {\it e}{\bf \o}rum ; *~conturb\ati sunt montes in fortit\u{\it dine} {\bf e}jus.}{Though its waters rage and foam * and the mountains quake at its surging.}

\lateng{0mm}{4 Fl\uminis \\i mpetus l\ae t\\i ficat ci\-vi\-t\a\-{\it tem} {\bf De}i: *~sanctific\avit ta\-ber\-n\a\-cu\-lum suum {\it Alt\\i s}{\bf si}mus.}{There is a stream whose runlets gladden the city of God, * the holy dwelling of the Most High.}

\lateng{0mm}{5 Deus in m\edio ejus, non com\-{\it mo}\-{\bf v\e}\-bitur; *~adjuv\abit eam Deus mane {\it dil\u}{\bf cu}lo.}{God is in its midst; it shall not be disturbed; * God will help it at the break of dawn.}

\lateng{0mm}{6 Conturb\at\ae \ sunt gentes, et inclin\ata {\it sunt} {\bf reg}na: *~dedit vocem suam, {\it mota} {\bf est} terra.}{Though nations are in turmoil, kingdoms totter, * His voice resounds, the earth melts away;}

\lateng{0mm}{7 D\ominus virt\utum {\it no}{\bf b\\i s}cum; *~susc\ep\-tor noster {\it Deus} {\bf Ja}cob.}{The Lord of hosts is with us; * our stronghold is the God of Jacob.}

\lateng{0mm}{8 Ven\\i te, et vid\ete \opera D\omini, \dag ~qu\ae \ p\osuit prod\\i gia su{\it per} {\bf ter}ram, *~\auferens bella usque ad {\it finem} {\bf ter}r\ae .}{Come, see the deeds of the Lord, \dag \ the astounding things He has wrought on earth, He has stopped wars to the end of the earth;}

\lateng{0mm}{9  Arcum c\onteret, et confr\\i n{\it get} {\bf ar}ma, *~et scuta com{\it b\uret} {\bf ig}ni.}{ * The bow he breaks; He splinters the spears; He burns the shields with fire.}

\lateng{0mm}{10 Vac\ate, et vid\ete qu\oniam ego {\it sum} {\bf De}us; *~exalt\abor in g\entibus, et exalt\a{\it bor in} {\bf ter}ra.}{Desist, and confess that I am God, * exalted among the nations, exalted upon the earth.}

\lateng{0mm}{11 D\ominus virt\utum {\it no}{\bf b\\i s}cum; *~sus\-c\ep\-tor noster {\it Deus} {\bf Ja}cob.}{The Lord of hosts is with us; * our stronghold is the God of Jacob.}

\lateng{0mm}{12 Gl\oria Patri, {\it et}  {\bf F\\i  }lio, *~et Spir\\i {\it tui} {\bf San}cto.}{Glory be to the Father, and to the Son, *~and to the Holy Spirit,}

\lateng{0mm}{13 Sicut erat in princ\\i pio, et nunc, {\it et} {\bf sem}per, *~et in s\\ae cula s\ae cu{\it l\orum.} {\bf A}men.}{As it was in the beginning, is now, and ever shall be, *~world without end. Amen.}